---
title: "Plotly_Asssignment"
author: "Shibashis Mukherjee"
date: "December 18, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

## Chatterjee Price Attitude Plot

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(plotly)
plot_ly(x = as.numeric(rownames(attitude)), y = attitude$rating, type="scatter", mode = "markers",  size=attitude$learning, color = attitude$complaints)
```

## Attitude Plot Explanation

- The Chatterjee Price attitude data shows the survey results from 35 clerical   employees about 30 departments of a large financial organization. The data contains ratings in seven different categories along with a overall rating for each department. 

- The plot is a scatter plot that shows the overall rating for each department with the departments on the X axis and rating on the Y axis. The size of the circles shows the rating forlearning opportunity and the color shows how well the department handled complaints.

## Thank You